Unified data structures to optimize solving a complex of interrelated geometric problems*\\

### 2019-11-17 article/article.tex
updated introduction 2

% previous work in the convex hull domain
The first known algorithm for solve the convex hull problem was introduces by Preparata in \cite{preparata}. Convex hull is maintained in a form of an AVL tree, that allows to perform operations of adding new points form it. The split and finding of tangents is performed in optimal time of $O(\log n)$. The major drawback of this method is that there is no mean to remote points from the set. Soon after Overmars and van Leeuwen described a method of how a concatenable queue can be used to maintain the convex hull \cite{overmars}. This, as well as special data structure that is based on a balanced binary tree and maintains the information gathered during previous queries, allows to support fully dynamic sets of points and perform add or remove query  $O(\log^2 n)$ in the worst case.

% scope of this article
In this article we solve \textcolor{red}{a collection of computational geometry problems} with a \textcolor{red}{generalized parallel-recursive} algorithm based on ``divide-and-conquer'' principle in $O(NlogN)$ time. We first describe how the algorithm can be applied to compute the convex hull. From there we consider several other problems where results gained from constructing the convex hull might be used. The partitioning stage of the initial points set is identical for all problems and the results of individual subproblems are maintained in the same data structure, namely, the concatenable queue. This yields good performance in comparison the approach, where intermediate results are recomputed every time.

@@

The notion of a convex hull is simple. For a set of points $S$ in a $k$-dimensional space it is a smallest convex set, that comprise $S$. The problem of building such a set has a long history. In practice to solve such problem, means to find a subset in $S$, which can be a "skeleton" for the convex hull.

It is differentiated between two types of point sets in this case: a static and a dynamic one. In the first case all points are known in advance. The algorithms for solving that kind of problem are well researched and described in \cite{jarvis, graham, quickhull}. In the letter case an algorithm should be able to handle new points which are being added to the initial set and some  being removed from it in real time. \textcolor{teal}{Initially a set of points can either contain points or be empty.}

>>>>

% previous work in the convex hull domain
For the convex hull problem it is differentiated between two types of point sets: a static and a dynamic one. In the first case all points are known in advance. The algorithms for solving that kind of problem are well researched and described in \cite{jarvis, graham, quickhull}. In the letter case an algorithm should be able to handle new points which are being added to the initial set and some  being removed from it in real time. The first known algorithm for solving such problem was introduces by Preparata in \cite{preparata}. Convex hull is maintained in a form of an AVL tree, that allows to perform operations of adding new points form it. The split and finding of tangents is performed in optimal time of $O(\log n)$. The major drawback of this method is that there is no mean to remote points from the set. Soon after Overmars and van Leeuwen described a method of how a concatenable queue can be used to maintain the convex hull \cite{overmars}. This, as well as special data structure that is based on a balanced binary tree and maintains the information gathered during previous queries, allows to support fully dynamic sets of points and perform add or remove query  $O(\log^2 n)$ in the worst case.

% scope of this article
In this article we solve \textcolor{red}{a collection of computational geometry problems} with a \textcolor{red}{generalized parallel-recursive} algorithm based on ``divide-and-conquer'' principle in $O(NlogN)$ time. We first describe how the algorithm can be applied to compute the convex hull. From there we consider several other problems where results gained from constructing the convex hull might be used. The partitioning stage of the initial points set is identical for all problems and the results of individual subproblems are maintained in the same data structure, namely, the concatenable queue. This yields good performance comparing to the case, where intermediate results are recomputed every time.

@@

The notion of a convex hull is simple. For a set of points $S$ in a $k$-dimensional space it is a smallest convex set, that comprise $S$. In practice to solve such problem, means to find a subset in $S$, which can be a "skeleton" for the convex hull.
